### 2019-11-07 otm1/results/analysis1.Rmd
Corrects some paths and knitts analysis for experiment 1 and supplements.

source("../../R/modal_frame_rate.R")

@@

@@

```{r otm1-bayesian-replication-analysis, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-design-matrix"}
# No effect model
otm1_no_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_null_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , nu = rep(1, otm1_n)
  )
  , rscale = c(fixed = 0.5, random = 1)
  , iterations = otm1_n_mcmc_samples
)

@@

```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, dependson = "otm1-bayesian-replication-analysis-unconstrained"}
# Fixed effect model
otm1_unconstrained_samples <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , posterior = TRUE
  , iterations = otm1_n_mcmc_samples
)
colnames(otm1_unconstrained_samples)[1:ncol(otm1_unconstrained_model_matrix) + 1] <- colnames(otm1_unconstrained_model_matrix)

otm1_unconstrained_samples <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  mutate(
    alpha_cologne = alpha + tau1
    , alpha_ghent =  alpha + tau1 - tau2
    , alpha_harvard = alpha - tau1 - tau2
    , beta_cologne = beta + upsilon1
    , beta_ghent = beta + upsilon1 - upsilon2
    , beta_harvard = beta - upsilon1 - upsilon2
  ) %>%
  as.matrix
```

@@

## Exploratory Analysis: Prime valence memory

```{r listPrimes, echo = FALSE, eval=FALSE}

>>>>

source("../../analysis_and_paper/modal_frame_rate.R")

@@

colnames(otm1_random_participant_intercept_matrix) <- paste0("ParticipantNumber", levels(otm1_attitudes_collapsed$ParticipantNumber))

@@

```{r otm1-bayesian-replication-analysis, cache = TRUE, dependson = "otm1-bayesian-replication-design-matrix"}
# No effect model
otm1_no_effect <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_null_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , nu = rep(1, otm1_n)
  )
  , rscale = c(fixed = 0.5, random = 1)
  , iterations = otm1_n_mcmc_samples
)

@@

```{r otm1-bayesian-replication-analysis-samples, cache = TRUE, dependson = "otm1-bayesian-replication-analysis"}
# Fixed effect model
otm1_unconstrained_samples <- nWayAOV(
  y = otm1_attitudes_collapsed$Attitude
  , X = otm1_unconstrained_model_matrix
  , gMap = c(
    eta = rep(0, 2)
    , alpha = 1, tau = rep(2, 2)
    , beta = 3, upsilon = rep(4, 2)
    , nu = rep(5, otm1_n)
  )
  , rscale = c(fixed = rep(0.5, 5), random = 1)
  , posterior = TRUE
  , iterations = otm1_n_mcmc_samples
)
colnames(otm1_unconstrained_samples)[1:ncol(otm1_unconstrained_model_matrix) + 1] <- colnames(otm1_unconstrained_model_matrix)
```

```{r}
otm1_unconstrained_samples <- otm1_unconstrained_samples %>%
  as.data.frame %>%
  mutate(
    alpha_cologne = alpha + tau1
    , alpha_ghent =  alpha + tau1 - tau2
    , alpha_harvard = alpha - tau1 - tau2
    , beta_cologne = beta + upsilon1
    , beta_ghent = beta + upsilon1 - upsilon2
    , beta_harvard = beta - upsilon1 - upsilon2
  ) %>%
  as.matrix
```

@@

<!-- ## Exploratory Analysis: Prime valence memory -->
```{r listPrimes, echo = FALSE, eval=FALSE}
